Building a GNU/Hurd Cluster

### 2018-01-29 slides/rpctrace.tex
slides - elisp code to modify \only macros appears to run properly

;; ELISP code to insert and remove slides from beamer \only macros
;;
;; XXX still have to deal with case where \only<2> needs to become \only<2-3> (inserting new frame 3)
;;     or \only<5> has to become \only<0> (deleting frame 5)

(defun incr-only-func (min)
  "increment all numbers in string greater than or equal to a minimum value"
  (let ((mystr (match-string 0)) (start 0) value)
       (save-match-data (while (string-match "[0-9]+" mystr start)
                               (setq value (string-to-number (match-string 0 mystr)))
                               (when (>= value min)
                                     (setq mystr (replace-match (number-to-string (1+ value))
                                                                nil nil mystr)))
                               (string-match "[0-9]+" mystr start)
                               (setq start (match-end 0))))
       mystr))

(defun incr-only (min)
  "increment an only macro"
  (interactive "NSlide number to insert: ")
  (query-replace-regexp "\\only<[^>]+>" `(replace-eval-replacement replace-quote (incr-only-func ,min))))

(defun decr-only-func (min)
  "decrement all numbers in string greater than a minimum value"
  (let ((mystr (match-string 0)) (start 0) value)
       (save-match-data (while (string-match "[0-9]+" mystr start)
                               (setq value (string-to-number (match-string 0 mystr)))
                               (when (> value min)
                                     (setq mystr (replace-match (number-to-string (1- value))
                                                                nil nil mystr)))
                               (string-match "[0-9]+" mystr start)
                               (setq start (match-end 0))))
       mystr))

(defun decr-only (min)
  "decrement an only macro"
  (interactive "NSlide number to remove: ")
  (query-replace-regexp "\\only<[^>]+>" `(replace-eval-replacement replace-quote (decr-only-func ,min))))

>>>>

;; ELISP code to insert and remove slides from beamer \only macros

(defun slide-func (slide)
  "add or remove a slide number from only macros"
  (let ((mystr (match-string 0)) (start 0) value1 value2 newstr (sign (/ slide (abs slide))))
       (save-match-data (while (string-match "\\([0-9]+\\)\\(-\\([0-9]+\\)?\\)?" mystr start)
                               (setq value1 (string-to-number (match-string 1 mystr)))
                               (setq value2 (cond ((match-string 3 mystr) (string-to-number (match-string 3 mystr)))
                                                  ((match-string 2 mystr) 1000000)
                                                  (t value1)))
                               (if (> value1 (abs slide)) (setq value1 (+ value1 sign)))
                               (if (>= value2 (abs slide)) (setq value2 (+ value2 sign)))
                               (setq newstr (cond ((> value1 value2) "0")
						  ((eq value1 value2) (format "%d" value1))
                                                  ((>= value2 999999) (format "%d-" value1))
                                                  (t (format "%d-%d" value1 value2))))
                               (setq mystr (replace-match newstr nil nil mystr))
                               (setq start (+ (match-beginning 0) (length newstr)))))
       mystr))

(defun slide-duplicate (slide)
  "remove slide numbers in only macros"
  (interactive "NSlide number to duplicate: ")
  (query-replace-regexp "\\only<[0-9-,]+>" `(replace-eval-replacement replace-quote (slide-func ,slide))))

(defun slide-remove (slide)
  "remove slide numbers from only macros"
  (interactive "NSlide number to remove: ")
  (query-replace-regexp "\\only<[0-9-,]+>" `(replace-eval-replacement replace-quote (slide-func ,(- slide)))))
